### 2025-03-07 analysis/analysis.qmd
chore(analysis): summarize feature n for study summaries and small code tweaks

```{r}
#| warning: false
#| eval: true
library(dmetar,quietly = TRUE)
library(tidyverse,quietly = TRUE)
library(meta)
library(DescTools)
library(ggrepel)
```

@@

@@

library(forestplot)
data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
data<-dplyr::arrange(data,mean)

@@

```{r}
m.cor1 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  model_class_id,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor1)
```

@@

```{r}
m.cor2 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  journal_type,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor2)
```

@@

```{r}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
print(S)

@@

m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  stimulus_genre_mixed,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
```

@@

```{r}
m.cor1 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  model_class_id,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor1)
```

@@

```{r}
m.cor2 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  journal_type,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor2)
```

@@

```{r}
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
print(S)

@@

m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  stimulus_genre_mixed,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
```

@@

@@

@@

library(forestplot)
data<-tibble::tibble(mean=m.cor.c$cor,lower=FisherZInv(m.cor.c$lower),upper=FisherZInv(m.cor.c$upper),study=m.cor.c$studlab,n=m.cor.c$n,cor=round(m.cor.c$cor,2))
data<-dplyr::arrange(data,mean)

@@

```{r}
library(ggrepel)
tmpdata <- data.frame(SE = FisherZInv(m.cor.c$seTE), Zr = FisherZInv(m.cor.c$TE),studies=m.cor.c$studlab)

@@

tmp2<-C_summary[!C_summary$studyREF %in% outliers,]
m.cor.c.o <- metacor(cor = valuesMax, 
                 n = stimulus_n,
                 studlab = tmp2$studyREF,
                 data = tmp2,
                 common = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 prediction = TRUE,
                 backtransf = TRUE,
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

@@

```{r}
m.cor_classes <- update(m.cor.c, 
       subgroup = C_summary$classes, 
       tau.common = FALSE,
       prediction = TRUE)

forest(m.cor_classes,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "N"),studlab = citekey)

@@

@@

```{r}
#| eval: false
m.cor_subgroups <- update(m.cor.c, 
       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)

@@

```{r}
m.cor_complexity <- update(m.cor.c,
       subgroup = C_summary$feature_n_complexity,
       tau.common = FALSE,
       prediction = TRUE)

@@

```{r}
#| eval: false
m.cor_subgroups <- update(m.cor.c, 
       subgroup = model_class_id, 
       tau.common = FALSE,
       prediction = TRUE)

>>>>

```{r}
#| warning: false
#| eval: true
library(dmetar,quietly = TRUE)
library(tidyverse,quietly = TRUE)
library(meta)
library(DescTools)
library(ggrepel)
library(forestplot)
```

@@

# print a summary of features

R_summary |> 
  group_by(feature_n_complexity) |> 
  summarize(min = min(feature_n), 
            max = max(feature_n), 
            mean = mean(feature_n), 
            mdn = median(feature_n))

@@

data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
data<-dplyr::arrange(data,mean)

@@

```{r}
m.cor1 <- update(m.cor,
       subgroup = model_class_id)
print(m.cor1)
```

@@

```{r}
m.cor2 <- update(m.cor,
       subgroup = journal_type)
print(m.cor2)
```

@@

```{r}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
m.cor3 <- update(m.cor,
       subgroup = feature_n_complexity)
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
print(S)

@@

m.cor4 <- update(m.cor,
       subgroup = stimulus_genre_mixed)

print(m.cor4)
```

@@

```{r}
m.cor1 <- update(m.cor,
                 subgroup = model_class_id
)
print(m.cor1)
```

@@

```{r}
m.cor2 <- update(
  m.cor,
  subgroup = journal_type
)
print(m.cor2)
```

@@

```{r}
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
m.cor3 <- update(
  m.cor,
  subgroup = feature_n_complexity
)
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
print(S)

@@

m.cor4 <- update(
  m.cor,
  subgroup = stimulus_genre_mixed
)

print(m.cor4)
```

@@

# print a summary of features

C_summary |> 
  group_by(feature_n_complexity) |> 
  summarize(min = min(feature_n), 
            max = max(feature_n), 
            mean = mean(feature_n), 
            mdn = median(feature_n))

@@

print(m.cor.c)

@@

data<-tibble::tibble(mean=m.cor.c$cor,lower=FisherZInv(m.cor.c$lower),upper=FisherZInv(m.cor.c$upper),study=m.cor.c$studlab,n=m.cor.c$n,cor=round(m.cor.c$cor,2))
data<-dplyr::arrange(data,mean)

@@

```{r}
tmpdata <- data.frame(SE = FisherZInv(m.cor.c$seTE), Zr = FisherZInv(m.cor.c$TE),studies=m.cor.c$studlab)

@@

tmp2<-C_summary[!C_summary$studyREF %in% outliers,]
m.cor.c.o <- metacor(cor = valuesMax, 
                 n = stimulus_n,
                 studlab = studyREF,
                 data = tmp2,
                 common = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 prediction = TRUE,
                 backtransf = TRUE,
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Classification: Summary")

@@

```{r}
m.cor_classes <- update(
  m.cor.c, 
  subgroup = classes)

print(m.cor_classes)

forest(m.cor_classes,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "N"),
       studlab = citekey)

@@

### By journal type

```{r}
m.cor_journal <- update(
  m.cor.c, 
  subgroup = journal_type
)

print(m.cor_journal)

@@

```{r}
#| eval: false
m.cor_subgroups <- update(
  m.cor.c, 
  subgroup = stimulus_genre_mixed
)

@@

```{r}
m.cor_complexity <- update(
  m.cor.c,
  subgroup = feature_n_complexity
)

@@

```{r}
#| eval: false
m.cor_subgroups <- update(
  m.cor.c, 
  subgroup = model_class_id, 
)
